Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-09-01 reanalysis-4-propensity_scores.qmd
testmode

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "final"  # Should match imputation mode

# PARALLEL PROCESSING CONFIGURATION
max_cores_for_ps <- 3  # Maximum cores to use for propensity score estimation (memory-intensive)

@@

# Function to process a single imputation
process_imputation <- function(i, imp_datasets, formula, trees, cache_path, use_caching, node_id, log_file_path) {
  # Recreate variables inside function to avoid scoping issues
  library(twang)

  # Log node start
  start_msg <- paste0("Node ", node_id, " started: Processing imputation ", i)
  cat(paste0(Sys.time(), " - ", start_msg, "\n"), file = log_file_path, append = TRUE)

@@

    # Log cache hit
    cache_msg <- paste0("Node ", node_id, " completed: Imputation ", i, " loaded from cache")
    cat(paste0(Sys.time(), " - ", cache_msg, "\n"), file = log_file_path, append = TRUE)

    return(list(
      imputation = i,
      node_id = node_id,
      result = cached_result,
      trees_used = cached_result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = TRUE,
      time_mins = 0
    ))
  } else {
    imp_start <- Sys.time()

@@

    # Log completion
    complete_msg <- paste0("Node ", node_id, " completed: Imputation ", i, " fitted in ", imp_time, " minutes")
    cat(paste0(Sys.time(), " - ", complete_msg, "\n"), file = log_file_path, append = TRUE)

    return(list(
      imputation = i,
      node_id = node_id,
      result = result,
      trees_used = result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = FALSE,
      time_mins = imp_time
    ))
  }
}

# Create assignments of imputations to node IDs
# Each imputation gets a unique sequential ID for tracking
imputation_node_assignments <- data.frame(
  imputation = 1:n_imputations,
  node_id = 1:n_imputations  # Simple sequential numbering: 1, 2, 3, 4, etc.
)

# Run parallel processing
log_message(paste0("Starting parallel processing of ", n_imputations, " imputations using ", n_cores, " cores"))
log_message(paste0("Node assignments: ", paste(imputation_node_assignments$node_id, collapse = ", ")))
parallel_start <- Sys.time()

# Use mclapply on Unix/Mac, parLapply on Windows
if (.Platform$OS.type == "unix") {
  # Unix/Mac - use mclapply
  parallel_results <- mclapply(
    1:n_imputations,
    function(i) {
      node_id <- imputation_node_assignments$node_id[i]
      process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, node_id, log_file)
    },
    mc.cores = n_cores
  )
} else {
  # Windows - use parLapply
  log_message(paste0("Creating cluster with ", n_cores, " workers"))
  cl <- makeCluster(n_cores)
  log_message(paste0("Cluster created with ", length(cl), " workers"))

  # Export necessary objects to cluster
  clusterExport(cl, c(
    "process_imputation", "imputed_datasets", "ps_formula", 
    "n_trees", "cache_dir", "use_cache", "imputation_node_assignments", "log_file"
  ), envir = environment())

@@

  # Create wrapper function for parLapply
  parallel_results <- parLapply(cl, 1:n_imputations, function(i) {
    node_id <- imputation_node_assignments$node_id[i]
    process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, node_id, log_file)
  })

@@

# Extract results and build progress dataframe
twang_results <- list()
progress_df <- data.frame(
  Imputation = integer(),
  Node_ID = integer(),
  Trees_Used = integer(),
  Weight_Min = numeric(),
  Weight_Max = numeric(),
  Cached = logical(),
  Time_Minutes = numeric()
)

@@

  progress_df <- rbind(progress_df, data.frame(
    Imputation = res$imputation,
    Node_ID = res$node_id,
    Trees_Used = res$trees_used,
    Weight_Min = res$weight_min,
    Weight_Max = res$weight_max,
    Cached = res$cached,
    Time_Minutes = res$time_mins
  ))

  # Log individual result summary
  if (res$cached) {
    log_message(paste0("Imputation ", res$imputation, " (Node ", res$node_id, "): Loaded from cache"))
  } else {
    log_message(paste0("Imputation ", res$imputation, " (Node ", res$node_id, "): Fitted in ", res$time_mins, " minutes"))
  }
}

@@

# Display progress summary with caching and timing information
kable(progress_df, 
      caption = paste0("Twang Model Fitting Progress (Total time: ", parallel_time, " minutes using ", n_cores, " cores)"),
      col.names = c("Imputation", "Node ID", "Trees Used", "Min Weight", "Max Weight", "From Cache", "Time (min)"))
```

>>>>

# ANALYSIS MODE: Use same as imputation
analysis_mode <- "test"  # Should match imputation mode

# PARALLEL PROCESSING CONFIGURATION
max_cores_for_ps <- 2  # Maximum cores to use for propensity score estimation (reduced for memory management)

@@

# Function to process a single imputation
process_imputation <- function(i, imp_datasets, formula, trees, cache_path, use_caching, worker_id, log_dir) {
  # Recreate variables inside function to avoid scoping issues
  library(twang)

  # Create worker-specific log file
  worker_log_file <- file.path(log_dir, paste0("propensity_scores_worker_", worker_id, ".log"))

  # Log start
  start_msg <- paste0("[Worker ", worker_id, "] Imputation ", i, " started")
  cat(paste0(Sys.time(), " - ", start_msg, "\n"), file = worker_log_file, append = TRUE)

@@

    # Log cache hit
    cache_msg <- paste0("[Worker ", worker_id, "] Imputation ", i, " loaded from cache")
    cat(paste0(Sys.time(), " - ", cache_msg, "\n"), file = worker_log_file, append = TRUE)

    return(list(
      imputation = i,
      worker_id = worker_id,
      result = cached_result,
      trees_used = cached_result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = TRUE,
      time_mins = 0,
      log_file = worker_log_file
    ))
  } else {
    imp_start <- Sys.time()

@@

    # Log completion
    complete_msg <- paste0("[Worker ", worker_id, "] Imputation ", i, " completed in ", imp_time, " minutes")
    cat(paste0(Sys.time(), " - ", complete_msg, "\n"), file = worker_log_file, append = TRUE)

    return(list(
      imputation = i,
      worker_id = worker_id,
      result = result,
      trees_used = result$n_trees_used,
      weight_min = round(min(weights), 3),
      weight_max = round(max(weights), 3),
      cached = FALSE,
      time_mins = imp_time,
      log_file = worker_log_file
    ))
  }
}

# Create log directory for worker logs
log_dir <- dirname(log_file)

# Create assignments of imputations to workers
# With 2 workers: Worker 1 gets 1-15, Worker 2 gets 16-30
worker_assignments <- data.frame(
  imputation = 1:n_imputations,
  worker_id = rep(1:n_cores, length.out = n_imputations)[1:n_imputations]
)

# For more even distribution with 2 workers
if (n_cores == 2) {
  midpoint <- ceiling(n_imputations / 2)
  worker_assignments$worker_id <- ifelse(worker_assignments$imputation <= midpoint, 1, 2)
}

# Run parallel processing
log_message(paste0("Starting parallel processing of ", n_imputations, " imputations using ", n_cores, " cores"))
log_message(paste0("Worker 1 will process imputations: ", 
                   paste(worker_assignments$imputation[worker_assignments$worker_id == 1], collapse = ", ")))
if (n_cores >= 2) {
  log_message(paste0("Worker 2 will process imputations: ", 
                     paste(worker_assignments$imputation[worker_assignments$worker_id == 2], collapse = ", ")))
}
parallel_start <- Sys.time()

# Use mclapply on Unix/Mac, parLapply on Windows
if (.Platform$OS.type == "unix") {
  # Unix/Mac - use mclapply
  parallel_results <- mclapply(
    1:n_imputations,
    function(i) {
      worker_id <- worker_assignments$worker_id[i]
      process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, worker_id, log_dir)
    },
    mc.cores = n_cores
  )
} else {
  # Windows - use parLapply
  log_message(paste0("Creating cluster with ", n_cores, " workers"))
  cl <- makeCluster(n_cores)
  log_message(paste0("Cluster created with ", length(cl), " workers"))

  # Export necessary objects to cluster
  clusterExport(cl, c(
    "process_imputation", "imputed_datasets", "ps_formula", 
    "n_trees", "cache_dir", "use_cache", "worker_assignments", "log_dir"
  ), envir = environment())

@@

  # Create wrapper function for parLapply
  parallel_results <- parLapply(cl, 1:n_imputations, function(i) {
    worker_id <- worker_assignments$worker_id[i]
    process_imputation(i, imputed_datasets, ps_formula, n_trees, cache_dir, use_cache, worker_id, log_dir)
  })

@@

# Extract results and build progress dataframe
twang_results <- list()
progress_df <- data.frame(
  Imputation = integer(),
  Worker_ID = integer(),
  Trees_Used = integer(),
  Weight_Min = numeric(),
  Weight_Max = numeric(),
  Cached = logical(),
  Time_Minutes = numeric()
)

@@

  progress_df <- rbind(progress_df, data.frame(
    Imputation = res$imputation,
    Worker_ID = res$worker_id,
    Trees_Used = res$trees_used,
    Weight_Min = res$weight_min,
    Weight_Max = res$weight_max,
    Cached = res$cached,
    Time_Minutes = res$time_mins
  ))

  # Log individual result summary in main log
  if (res$cached) {
    log_message(paste0("Imputation ", res$imputation, " (Worker ", res$worker_id, "): Loaded from cache"))
  } else {
    log_message(paste0("Imputation ", res$imputation, " (Worker ", res$worker_id, "): Fitted in ", res$time_mins, " minutes"))
  }
}

# Read and consolidate worker logs
log_message("=== Worker Log Summary ===")
for (worker in 1:n_cores) {
  worker_log_file <- file.path(log_dir, paste0("propensity_scores_worker_", worker, ".log"))
  if (file.exists(worker_log_file)) {
    worker_logs <- readLines(worker_log_file)
    log_message(paste0("Worker ", worker, " processed ", 
                      sum(grepl("started", worker_logs)), " imputations, ",
                      sum(grepl("completed", worker_logs)), " completed"))
    # Optionally show first and last entries
    if (length(worker_logs) > 0) {
      log_message(paste0("  First: ", worker_logs[1]))
      log_message(paste0("  Last:  ", worker_logs[length(worker_logs)]))
    }
  }
}
log_message("==========================")

@@

# Display progress summary with caching and timing information
kable(progress_df, 
      caption = paste0("Twang Model Fitting Progress (Total time: ", parallel_time, " minutes using ", n_cores, " cores)"),
      col.names = c("Imputation", "Worker", "Trees Used", "Min Weight", "Max Weight", "From Cache", "Time (min)"))
```

### 2025-09-01 reanalysis-5-outcome_analysis.qmd
testmode

# Display the convergence table (first 10 and last 10 if more than 20)
if (n_imputations > 20) {
  convergence_display <- rbind(
    head(imputation_estimates, 10),
    data.frame(imputation = "...", log_odds = "...", OR = "...", running_avg_OR = "..."),
    tail(imputation_estimates, 10)
  )
} else {
  convergence_display <- imputation_estimates
}

>>>>

# Display the convergence table (first 10 and last 10 if more than 20)
convergence_display <- imputation_estimates
